A Data-Driven Framework for Neural Field Modeling

### 2011-01-14 ltx/first_order_framework/response_to_reviews.tex

    \end{enumerate}

    \section{Reviewer 2}

    We thank the reviewer for their encouraging review. Each point raised is dealt with in turn.

\begin{enumerate}
    \item The handling of the (to borrow a term from numerical weather forecasting) `sub-grid scale physics' is inadequate for nervous systems (see, e.g., equation 8 \parham{(now equation 12)} [The nonlinear IntegroDifference Equation]). I do very much appreciate the spectral estimation of spatial and temporal scales. But the model errors are lumped into an iid model error term that is not realistic. For instance, the flow of potassium in the extracellular spaces has a known dynamic that will affect network excitability, generating important sub-grid dynamics that is anything but iid. See, for instance, the example in Ullah et al PLoS Comp Biol 2010 where without such dynamics, state tracking and parameter estimation for a neural system fails. A beautiful overview of sub-grid effects in data assimilation is found in Kalnay's 2003 book. I would very much value the authors comments on these issues. I guess were I to respond to this question, that I might consider extending the model error term to an autoregressive model. But I will let the authors answer this question.

@@

	\emph{\parham{The authors believe that allowing for time-varying parameters will account for changes in excitability levels. In future work, we will also estimate the disturbance properties (spatial covariance and temporal variance). To address this point in this paper, we have added an extra paragraph to `Neural Field Model' section of the Methods, where we discuss the model mismatch and some basic modeling assumptions, such as stationarity of the parameters. In addition, we have added to the discussion (Extensions section) with possible ways to relax these assumptions.}}

\item Although we all know the 1970s version of Wilson and Cowan's field equations, there was an intriguing stochasticization of these equations by Benayoun et al PloS Comp Biol 2010. I and others will value the authors' thoughts of how a more palatable stochasticization of these field equations might influence the future development of the data-assimilation framework presented in this paper.

\dean{\emph{The results of Benayoun et al. provide evidence that the variance in a stochastic WC model will depend on the number of neurons that are modeled (in a stochastic network), where a larger network behaves more like the deterministic WC equations. This work encourages the use of the WC model for data-assimilation, but provides evidence that the disturbance properties should also be estimated. The authors believe that estimating the noise properties is possible, and we are planning to demonstrate how to achieve this in a subsequent paper. We have added some comments to the Extension to the Framework section in this regard.}}

### 2011-01-14 ltx/first_order_framework/LaTeX_Manuscript.tex
comment on spatial frequency in discussion

\dean{(Reviewer 2, comment 6:) The work of \citet{Freeman2000} provides direct evidence that the electrode spatial frequency of the neural field is in the range of 0.1-0.4 cycles/mm and spacing required to prevent aliasing is approximately 1.25 mm. Micro-electrodes systems that satisfy this requirement are now currently in for brain computer interface and epilepsy monitoring applications~\citep{Cheung2007}, which suggests that the framework can be applied to humans with existing technology.}

>>>>

\dean{(Reviewer 2, comment 6:) The work of \citet{Freeman2000} provides direct evidence that the \parham{electrode} spatial frequency of the neural field is in the range of 0.1-0.4 cycles/mm and spacing required to prevent aliasing is approximately 1.25 mm. Micro-electrodes systems that satisfy this requirement are now currently in for brain computer interface and epilepsy monitoring applications~\citep{Cheung2007}, which suggests that the framework can be applied to humans with existing technology.}
